\huge Platform for Anomaly Detection in Time-Series

### 2018-11-05 article.tex
Started doing tests
Man, I am really falling behind on this crap.

\subsection{Anomalous Time Series Detection}

@@

In this section we will perform some experiments on some data, but we have not yet decided what we are going to do.

>>>>

@@

In this section we will compare a number of anomaly detection methods, and compare their results. \\

We will use precision and recall to compare the methodologies presented.

First dataset

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{testplot1}   
\caption{Description pending.}
\label{fig:test1}
\end{figure}

\begin{center}
\begin{tabular}{| c | c | c |}
\hline
Method                      & Precision & Recall \\ \hline
Bounded Derrivative (d = 0) & 1         & 0.3678 \\ \hline
Bounded Derrivative (d = 1) & 0.6       & 0.0689 \\ \hline
Median Method               & 0.33      & 0.0919 \\ \hline
\end{tabular}
\end{center}
